A Survey of Real-Time Strategy Game AI\\ Research and Competition in StarCraft

### 2013-03-16 survey.tex
Fixed a couple of typos

A typical StarCraft map is defined as a rectangular grid, where the $width \times height$ of the map is measured in the number of $32 \times 32$ square of pixels, also knows as build tiles. Although the
resolution of walkable areas is in squares of $8 \times 8$ pixels, also knows as walk tiles. The typical dimensions for maps range from $64 \times 64$ to $256 \times 256$ build tiles. Each player  can
control up  to 200 units (plus an unlimited number of buildings).  Moreover, each
different race  contains between 30  to 35 different types  of units
and  buildings,  each  one  with  a significant  number  of  special
abilities. All these factors  together make StarCraft a significant
challenge,   in   which   humans    are   still   much   better   than
computers. For instance, in the game ladder iCCup\footnote{http://www.iccup.com/StarCraft/} where users are ranked by their current point totals ($E$ being the lowest possible rank, and $A^+$ and $Olympic$ being the second highest and highest ranks, respectively), the best StarCraft AI bots are ranked between $D$ and $D^+$, where average  amateur players are  ranked between $C^+$ and  $B$. For comparison, StarCraft professional  players are usually ranked between
$A^-$ and $A^+$.

@@

As the list in the previous section indicates, Real-Time Strategy games are an excellent testbed for AI techniques, which pose a very large list of open problems. As Section \ref{sec:competition} has shown, the current top performing programs to play RTS games such as StarCraft still rely mainly on hard-coded strategies. It is still possible to perform strongly, or even win, one of these competitions simply by finding a hard-coded strategy that no other bot has a predefined counter-strategy for. Additionally, good human players are still clearly superior to the best computer programs. From an industry point of view, one additional challenge is to make bots more believable to play against, and thus, more fun for human players (this includes, for example, doing actual scouting, instead of cheating and having full information of the game state).

>>>>

A typical StarCraft map is defined as a rectangular grid, where the $width \times height$ of the map is measured in the number of $32 \times 32$ square of pixels, also known as build tiles. Although the
resolution of walkable areas is in squares of $8 \times 8$ pixels, also known as walk tiles. The typical dimensions for maps range from $64 \times 64$ to $256 \times 256$ build tiles. Each player  can
control up  to 200 units (plus an unlimited number of buildings).  Moreover, each
different race  contains between 30  to 35 different types  of units
and  buildings,  each  one  with  a significant  number  of  special
abilities. All these factors  together make StarCraft a significant
challenge,   in   which   humans    are   still   much   better   than
computers. For instance, in the game ladder iCCup\footnote{http://www.iccup.com/StarCraft/} where users are ranked by their current point totals ($E$ being the lowest possible rank, and $A^+$ and $Olympic$ being the second highest and highest ranks, respectively), the best StarCraft AI bots are ranked between $D$ and $D^+$, where average  amateur players are  ranked between $C^+$ and  $B$. For comparison, StarCraft professional  players are usually ranked between
$A^-$ and $A^+$.

@@

As the list in the previous section indicates, Real-Time Strategy games are an excellent testbed for AI techniques, which pose a very large list of open problems. As Section \ref{sec:competition} has shown, the current top performing programs to play RTS games such as StarCraft still rely mainly on hard-coded strategies. It is still possible to perform strongly, or even win, one of these competitions simply by finding a hard-coded strategy that no other bot has a predefined counter-strategy for. Additionally, good human players are still clearly superior to the best computer programs. From an industry point of view, one additional challenge is to make bots more believable to play against, and thus, more fun for human players (this includes, for example, doing scouting, instead of cheating and having full information of the game state).
